### 2023-01-19 abstract-intro/paper.tex
Day1

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\begin{Lowcost}

\title{Conference Paper Title*\\
{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
should not be used}
\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
}

\maketitle

\begin{abstract}
This document is a model and instructions for \LaTeX.
This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes,
or Math in Paper Title or Abstract.
\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

\section{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the conference page limits.

\section{Ease of Use}

\subsection{Maintaining the Integrity of the Specifications}

The IEEEtran class file is used to format your paper and style the text. All margins,
column widths, line spaces, and text fonts are prescribed; please do not
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement
and others are deliberate, using specifications that anticipate your paper
as one part of the entire proceedings, and not as an independent document.
Please do not revise any of the current designations.

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a
separate text file. Complete all content and organizational editing before
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on
proofreading, spelling and grammar.

Keep your text and graphic files separate until after the text has been
formatted and styled. Do not number text heads---{\LaTeX} will do that
for you.

\subsection{Abbreviations and Acronyms}\label{AA}
Define abbreviations and acronyms the first time they are used in the text,
even after they have been defined in the abstract. Abbreviations such as
IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use
abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}
\begin{itemize}
\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\subsection{Equations}
Number equations consecutively. To make your
equations more compact, you may use the solidus (~/~), the exp function, or
appropriate exponents. Italicize Roman symbols for quantities and variables,
but not Greek symbols. Use a long dash rather than a hyphen for a minus
sign. Punctuate equations with commas or periods when they are part of a
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the
symbols in your equation have been defined before or immediately following
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Authors and Affiliations}
\textbf{The class file is designed for, but not limited to, six authors.} A
minimum of one author is required for all conference articles. Author names
should be listed starting from left to right and then moving down to the
next line. This is the author sequence that will be used in future citations
and by indexing services. Names should not be listed in columns nor group by
affiliation. Please keep your affiliations as succinct as possible (for
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}
Headings, or heads, are organizational devices that guide the reader through
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not
topically subordinate to each other. Examples include Acknowledgments and
References and, for these, the correct style to use is ``Heading 5''. Use
``figure caption'' for your Figure captions, and ``table head'' for your
table title. Run-in heads, such as ``Abstract'', will require you to apply a
style (in this case, italic) in addition to the style provided by the drop
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For
example, the paper title is the primary text head because all subsequent
material relates and elaborates on this one topic. If there are two or more
sub-topics, the next level head (uppercase Roman numerals) should be used
and, conversely, if there are not at least two sub-topics, then no subheads
should be introduced.

\subsection{Figures and Tables}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and
bottom of columns. Avoid placing them in the middle of columns. Large
figures and tables may span across both columns. Figure captions should be
below the figures; table heads should appear above the tables. Insert
figures and tables after they are cited in the text. Use the abbreviation
``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4}
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\begin{figure}[htbp]
\centerline{\includegraphics{fig1.png}}
\caption{Example of a figure caption.}
\label{fig}
\end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words
rather than symbols or abbreviations when writing Figure axis labels to
avoid confusing the reader. As an example, write the quantity
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including
units in the label, present them within parentheses. Do not label axes only
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of
quantities and units. For example, write ``Temperature (K)'', not
``Temperature/K''.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B.
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor
acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at
the bottom of the column in which it was cited. Do not put footnotes in the
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use
``et al.''. Papers that have not been published, even if they have been
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers
that have been accepted for publication should be cited as ``in press'' \cite{b5}.
Capitalize only the first word in a paper title, except for proper nouns and
element symbols.

For papers published in translation journals, please give the English
citation first, followed by the original foreign-language citation \cite{b6}.

\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

\end{document}

### 2023-02-14 abstract-intro/paper.tex
edited paper.tex

@@
 \documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
+%\IEEEoverridecommandlockouts
 % The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
@@
 
-\begin{Lowcost}
+\begin{document}
 
-\title{Conference Paper Title*\\
-{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
-should not be used}
-\thanks{Identify applicable funding agency here. If none, delete this.}
-}
+    \title{Low cost IOT based cloud solution for Intelligence Integrated Black fly rearing.}
 
-\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
+    \author{
+
+        \IEEEauthorblockN{1\textsuperscript{st} Shawal Mbalire}
+        \IEEEauthorblockA{\textit{School of Engineering,CEDAT} \\
+        \textit{Makerere University}\\
+        Kampala, Uganda \\
+        mshawal49@icloud.com}
+
         \and
-\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
+        \IEEEauthorblockN{2\textsuperscript{nd} Mary Patience Namugwanya}
+        \IEEEauthorblockA{\textit{School of Engineering,CEDAT} \\
+        \textit{Makerere University}\\
+        Kampala, Uganda \\
+        nmarypatience@gmail.com}
+
         \and
-\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
-\and
-\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
-\and
-\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
-\and
-\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
+        \IEEEauthorblockN{3\textsuperscript{rd} Bradley Alfred Mpeera Tuwmine}
+        \IEEEauthorblockA{\textit{School of Engineering,CEDAT} \\
+        \textit{Makerere University}\\
+        Kampala, Uganda \\
+        bradleytumwine82@gmail.com}
     }
@@
     \begin{abstract}
-This document is a model and instructions for \LaTeX.
-This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes,
-or Math in Paper Title or Abstract.
+        This paper aims to increase the production of black fly larvae for farmers to scale up by automating the monotonous and monitoring intesive tasks.
     \end{abstract}
@@
     \begin{IEEEkeywords}
-component, formatting, style, styling, insert
+        black fly soldier fly larvea,iot
     \end{IEEEkeywords}
@@
     \section{Introduction}
-This document is a model and instructions for \LaTeX.
-Please observe the conference page limits.
-
-\section{Ease of Use}
-
-\subsection{Maintaining the Integrity of the Specifications}
-
-The IEEEtran class file is used to format your paper and style the text. All margins,
-column widths, line spaces, and text fonts are prescribed; please do not
-alter them. You may note peculiarities. For example, the head margin
-measures proportionately more than is customary. This measurement
-and others are deliberate, using specifications that anticipate your paper
-as one part of the entire proceedings, and not as an independent document.
-Please do not revise any of the current designations.
-
-\section{Prepare Your Paper Before Styling}
-Before you begin to format your paper, first write and save the content as a
-separate text file. Complete all content and organizational editing before
-formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on
-proofreading, spelling and grammar.
-
-Keep your text and graphic files separate until after the text has been
-formatted and styled. Do not number text heads---{\LaTeX} will do that
-for you.
-
-\subsection{Abbreviations and Acronyms}\label{AA}
-Define abbreviations and acronyms the first time they are used in the text,
-even after they have been defined in the abstract. Abbreviations such as
-IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use
-abbreviations in the title or heads unless they are unavoidable.
-
-\subsection{Units}
-\begin{itemize}
-\item Use either SI (MKS) or CGS as primary units.
-(SI units are encouraged.) English units may be used as secondary units (in parentheses).
-An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
-\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
-This often leads to confusion because equations do not balance dimensionally.
-If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
-Spell out units when they appear in text: ``.
-.
-.
-a few henries'', not ``.
-.
-.
-a few H''.
-\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
-\end{itemize}
-
-\subsection{Equations}
-Number equations consecutively. To make your
-equations more compact, you may use the solidus (~/~), the exp function, or
-appropriate exponents. Italicize Roman symbols for quantities and variables,
-but not Greek symbols. Use a long dash rather than a hyphen for a minus
-sign. Punctuate equations with commas or periods when they are part of a
-sentence, as in:
-\begin{equation}
-a+b=\gamma\label{eq}
-\end{equation}
-
-Be sure that the
-symbols in your equation have been defined before or immediately following
-the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at
-the beginning of a sentence: ``Equation \eqref{eq} is . . .''
-
-\subsection{\LaTeX-Specific Advice}
-
-Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
-of ``hard'' references (e.g., \verb|(1)|). That will make it possible
-to combine sections, add equations, or change the order of figures or
-citations without having to go through the file line by line.
-
-Please don't use the \verb|{eqnarray}| equation environment. Use
-\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
-environment leaves unsightly spaces around relation symbols.
-
-Please note that the \verb|{subequations}| environment in {\LaTeX}
-will increment the main equation counter even when there are no
-equation numbers displayed. If you forget that, you might write an
-article in which the equation numbers skip from (17) to (20), causing
-the copy editors to wonder if you've discovered a new method of
-counting.
-
-{\BibTeX} does not work by magic. It doesn't get the bibliographic
-data from thin air but from .bib files. If you use {\BibTeX} to produce a
-bibliography you must send the .bib files.
-
-{\LaTeX} can't read your mind. If you assign the same label to a
-subsubsection and a table, you might find that Table I has been cross
-referenced as Table IV-B3.
-
-{\LaTeX} does not have precognitive abilities. If you put a
-\verb|\label| command before the command that updates the counter it's
-supposed to be using, the label will pick up the last counter to be
-cross referenced instead. In particular, a \verb|\label| command
-should not go before the caption of a figure or a table.
-
-Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
-will not stop equation numbers inside \verb|{array}| (there won't be
-any anyway) and it might stop a wanted equation number in the
-surrounding equation.
-
-\subsection{Some Common Mistakes}\label{SCM}
-\begin{itemize}
-\item The word ``data'' is plural, not singular.
-\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
-\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
-When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
-A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within the parentheses.)
-\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
-\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
-\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
-\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
-\item Do not confuse ``imply'' and ``infer''.
-\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
-\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
-\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
-\end{itemize}
-An excellent style manual for science writers is \cite{b7}.
-
-\subsection{Authors and Affiliations}
-\textbf{The class file is designed for, but not limited to, six authors.} A
-minimum of one author is required for all conference articles. Author names
-should be listed starting from left to right and then moving down to the
-next line. This is the author sequence that will be used in future citations
-and by indexing services. Names should not be listed in columns nor group by
-affiliation. Please keep your affiliations as succinct as possible (for
-example, do not differentiate among departments of the same organization).
-
-\subsection{Identify the Headings}
-Headings, or heads, are organizational devices that guide the reader through
-your paper. There are two types: component heads and text heads.
-
-Component heads identify the different components of your paper and are not
-topically subordinate to each other. Examples include Acknowledgments and
-References and, for these, the correct style to use is ``Heading 5''. Use
-``figure caption'' for your Figure captions, and ``table head'' for your
-table title. Run-in heads, such as ``Abstract'', will require you to apply a
-style (in this case, italic) in addition to the style provided by the drop
-down menu to differentiate the head from the text.
-
-Text heads organize the topics on a relational, hierarchical basis. For
-example, the paper title is the primary text head because all subsequent
-material relates and elaborates on this one topic. If there are two or more
-sub-topics, the next level head (uppercase Roman numerals) should be used
-and, conversely, if there are not at least two sub-topics, then no subheads
-should be introduced.
-
-\subsection{Figures and Tables}
-\paragraph{Positioning Figures and Tables} Place figures and tables at the top and
-bottom of columns. Avoid placing them in the middle of columns. Large
-figures and tables may span across both columns. Figure captions should be
-below the figures; table heads should appear above the tables. Insert
-figures and tables after they are cited in the text. Use the abbreviation
-``Fig.~\ref{fig}'', even at the beginning of a sentence.
-
-\begin{table}[htbp]
-\caption{Table Type Styles}
-\begin{center}
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-\cline{2-4}
-\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
-\hline
-copy& More table copy$^{\mathrm{a}}$& &  \\
-\hline
-\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
-\end{tabular}
-\label{tab1}
-\end{center}
-\end{table}
-
-\begin{figure}[htbp]
-\centerline{\includegraphics{fig1.png}}
-\caption{Example of a figure caption.}
-\label{fig}
-\end{figure}
-
-Figure Labels: Use 8 point Times New Roman for Figure labels. Use words
-rather than symbols or abbreviations when writing Figure axis labels to
-avoid confusing the reader. As an example, write the quantity
-``Magnetization'', or ``Magnetization, M'', not just ``M''. If including
-units in the label, present them within parentheses. Do not label axes only
-with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization
-\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of
-quantities and units. For example, write ``Temperature (K)'', not
-``Temperature/K''.
-
-\section*{Acknowledgment}
-
-The preferred spelling of the word ``acknowledgment'' in America is without
-an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B.
-G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor
-acknowledgments in the unnumbered footnote on the first page.
-
-\section*{References}
-
-Please number citations consecutively within brackets \cite{b1}. The
-sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference
-number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at
-the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
-
-Number footnotes separately in superscripts. Place the actual footnote at
-the bottom of the column in which it was cited. Do not put footnotes in the
-abstract or reference list. Use letters for table footnotes.
-
-Unless there are six authors or more give all authors' names; do not use
-``et al.''. Papers that have not been published, even if they have been
-submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers
-that have been accepted for publication should be cited as ``in press'' \cite{b5}.
-Capitalize only the first word in a paper title, except for proper nouns and
-element symbols.
-
-For papers published in translation journals, please give the English
-citation first, followed by the original foreign-language citation \cite{b6}.
-
-\begin{thebibliography}{00}
-\bibitem{b1} G.
-Eason, B.
-Noble, and I.
-N.
-Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil.
-Trans.
-Roy.
-Soc.
-London, vol.
-A247, pp.
-529--551, April 1955.
-\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
-\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
-\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
-\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
-\bibitem{b6} Y.
-Yorozu, M.
-Hirano, K.
-Oka, and Y.
-Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl.
-J.
-Magn.
-Japan, vol.
-2, pp.
-740--741, August 1987 [Digests 9th Annual Conf.
-Magnetics Japan, p.
-301, 1982].
-\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
-\end{thebibliography}
-\vspace{12pt}
-\color{red}
-IEEE conference templates contain guidance text for composing and formatting conference papers.
-Please ensure that all template text is removed from your conference paper prior to submission to the conference.
-Failure to remove the template text from your paper may result in your paper not being published.
 

### 2023-02-25 abstract-intro/paper.tex
Update paper.tex

@@
     \begin{abstract}
-        This paper aims to increase the production of black fly larvae for farmers to scale up by automating the monotonous and monitoring intesive tasks.
+       Black soldier fly(BSF), Hermetia illucens is a commonly and widespread fly of the family Stratiomyidae.
+Since the late 20th century, its larvae stage has increasingly gained attention due to its effective bio-waste conversion.
+Additionally, it has an excellent ability to transform waste into high quality protein.
+Used as alternative protein additives in animal feed, this translates into an inexpensive clean and sustainable food source.
+Though effective, it requires certain environmental conditions that needs to be monitored regularly to make sure the larvae can process the waste effectively.
+Additionally, several challenges remain to ensure that BSF farming is economically viable at different scales and can be widely implemented.
+Manual labor is required to ensure optimal conditions to rear the larvae, from aerating the feeding substrate to monitoring abiotic conditions during the growth cycle.
+But, BSF farmers are not always on site and the human resource is limited.
+Thus, an automated system with a remote monitoring capability is needed to ease the monitoring process.
+This paper proposes the Internet of Things (IoT) for environmental condition monitoring to ensure optimal growing conditions and data collection from the sensors to be obtained in real-time.
     \end{abstract}
@@
     \begin{IEEEkeywords}
-        black fly soldier fly larvea,iot
+        black soldier fly ,iot
     \end{IEEEkeywords}
@@
     \section{Introduction}
+Bio-waste management is one of the main global challenges of our time, with significant repercussions on human and environmental health related to sanitary issues, pollution of ground water, and emission of greenhouse gases (GHGs).
+As global population and consumption rise, bio-waste production is also projected to increase significantly.
+Conventional methods of dealing with bio-waste, including open dumping in less economically developed countries or landfilling not equipped with means to capture GHGs such as methane, exacerbate the global warming crisis.
+Besides, landfills release various odors, attract disease vectors, and produce leachates that pollute ground water.
+Black soldier fly (BSF), Hermetia illucens, is an insect that has gained popularity among other insect-based bio-waste treatments for its effectiveness to convert bio-waste using its larvae.
+Bio-waste biomass is consumed by the larvae, which then will be transformed into protein and fat of the larvae as well as its residue.
+The larvae is known to be having a high quality protein suitable for feeding chicken and fish, residue contains nutrients and organic matter that helps reduce soil depletion.
+Additionally, its effectiveness in reducing the risk of bacterial transmission through bio-waste makes BSF a safe option for bio-waste treatment in farm level.
+Previously, BSF farming required wide spaces about 150 m2 that made it difficult to rear in locations with limited spaces like urban areas.
+Moreover, the rearing method needs special care to adjust suitable condition (temperature and humidity) and frequent attention from laborers which generally take times in each procedure.
+For this reason, there was a need to establish an intelligent BSF rearing system.
+The Internet of Things (IoT) has begun to emerge as it has helped human in controlling and monitoring essential conditions using devices which are able to capture, evaluate and transmit information from the environment to the cloud, where the data will be stored.
+Environment monitoring system is one of the most important IoT systems which mainly includes data collections through sensors and data reviewing for short-term measure as well as remote management and observations.
+By using the IoT system to maintain the environmental condition i.e.
+temperature, relative humidity, light intensity and aeration of BSF larvae on its optimum level, data collection from the sensors needs to be obtained in real time to make sure that the data is accurate and representing the exact information of the environmental condition, as well as to be saved automatically to the database for certain period.
+This is to ensure that the user will have the proper information to interpret the insect’s environmental condition.
+Thus, data communication from the sensor to the database plays an important role in obtaining this need.
+This paper seeks to develop an automated solution to BSF rearing addressing two needs:
+\begin{enumerate}
+\item Controlling the environmental conditions, which is currently manual and labor-intensive. 
+\item Remote monitoring of these conditions in real time.
+\end{enumerate}
 

### 2023-02-26 abstract-intro/paper.tex
paper.tex updated

@@
 \author{
-
-        \IEEEauthorblockN{1\textsuperscript{st} Shawal Mbalire}
+    \IEEEauthorblockN{1\textsuperscript{st} Bradley Alfred Mpeera Tuwmine}
     \IEEEauthorblockA{\textit{School of Engineering,CEDAT} \\
@@
         Kampala, Uganda \\
-        mshawal49@icloud.com}
+        bradleytumwine82@gmail.com}
 
     \and
-        \IEEEauthorblockN{2\textsuperscript{nd} Mary Patience Namugwanya}
+    \IEEEauthorblockN{2\textsuperscript{nd} Frank Ssemakula}
+    \IEEEauthorblockA{\textit{School of Engineering,CEDAT} \\
+        \textit{Makerere University}\\
+        Kampala, Uganda \\
+        dashdash@gmail.com}
+
+    \and
+    \IEEEauthorblockN{3\textsuperscript{rd} Mary Patience Namugwanya}
     \IEEEauthorblockA{\textit{School of Engineering,CEDAT} \\
@@
     \and
-        \IEEEauthorblockN{3\textsuperscript{rd} Bradley Alfred Mpeera Tuwmine}
+    \IEEEauthorblockN{4\textsuperscript{th} Shawal Mbalire}
     \IEEEauthorblockA{\textit{School of Engineering,CEDAT} \\
@@
         Kampala, Uganda \\
-        bradleytumwine82@gmail.com}
+        mshawal49@icloud.com}\hspace{\linewidth}
+
 }
@@
 \begin{abstract}
-       Black soldier fly(BSF), Hermetia illucens is a commonly and widespread fly of the family Stratiomyidae.
-Since the late 20th century, its larvae stage has increasingly gained attention due to its effective bio-waste conversion.
-Additionally, it has an excellent ability to transform waste into high quality protein.
-Used as alternative protein additives in animal feed, this translates into an inexpensive clean and sustainable food source.
-Though effective, it requires certain environmental conditions that needs to be monitored regularly to make sure the larvae can process the waste effectively.
-Additionally, several challenges remain to ensure that BSF farming is economically viable at different scales and can be widely implemented.
-Manual labor is required to ensure optimal conditions to rear the larvae, from aerating the feeding substrate to monitoring abiotic conditions during the growth cycle.
-But, BSF farmers are not always on site and the human resource is limited.
-Thus, an automated system with a remote monitoring capability is needed to ease the monitoring process.
-This paper proposes the Internet of Things (IoT) for environmental condition monitoring to ensure optimal growing conditions and data collection from the sensors to be obtained in real-time.
+    This paper aims to increase the production of black fly larvae for farmers to scale up by automating the monotonous and monitoring intesive tasks.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-        black soldier fly ,iot
+    black fly soldier fly larvea,iot
 \end{IEEEkeywords}
+\section{Introduction}
 
-    \section{Introduction}
-Bio-waste management is one of the main global challenges of our time, with significant repercussions on human and environmental health related to sanitary issues, pollution of ground water, and emission of greenhouse gases (GHGs).
-As global population and consumption rise, bio-waste production is also projected to increase significantly.
-Conventional methods of dealing with bio-waste, including open dumping in less economically developed countries or landfilling not equipped with means to capture GHGs such as methane, exacerbate the global warming crisis.
-Besides, landfills release various odors, attract disease vectors, and produce leachates that pollute ground water.
-Black soldier fly (BSF), Hermetia illucens, is an insect that has gained popularity among other insect-based bio-waste treatments for its effectiveness to convert bio-waste using its larvae.
-Bio-waste biomass is consumed by the larvae, which then will be transformed into protein and fat of the larvae as well as its residue.
-The larvae is known to be having a high quality protein suitable for feeding chicken and fish, residue contains nutrients and organic matter that helps reduce soil depletion.
-Additionally, its effectiveness in reducing the risk of bacterial transmission through bio-waste makes BSF a safe option for bio-waste treatment in farm level.
-Previously, BSF farming required wide spaces about 150 m2 that made it difficult to rear in locations with limited spaces like urban areas.
-Moreover, the rearing method needs special care to adjust suitable condition (temperature and humidity) and frequent attention from laborers which generally take times in each procedure.
-For this reason, there was a need to establish an intelligent BSF rearing system.
-The Internet of Things (IoT) has begun to emerge as it has helped human in controlling and monitoring essential conditions using devices which are able to capture, evaluate and transmit information from the environment to the cloud, where the data will be stored.
-Environment monitoring system is one of the most important IoT systems which mainly includes data collections through sensors and data reviewing for short-term measure as well as remote management and observations.
-By using the IoT system to maintain the environmental condition i.e.
-temperature, relative humidity, light intensity and aeration of BSF larvae on its optimum level, data collection from the sensors needs to be obtained in real time to make sure that the data is accurate and representing the exact information of the environmental condition, as well as to be saved automatically to the database for certain period.
-This is to ensure that the user will have the proper information to interpret the insect’s environmental condition.
-Thus, data communication from the sensor to the database plays an important role in obtaining this need.
+Bio-waste management is one of the main global challenges of our time, with significant
+repercussions on human and environmental health related to sanitary issues, pollution of ground
+water, and emission of greenhouse gases (GHGs). As global population and consumption rise, biowaste production is also projected to increase significantly. Conventional methods of dealing with
+bio-waste, including open dumping in less economically developed countries or landfilling not
+equipped with means to capture GHGs such as methane, exacerbate the global warming crisis.
+Besides, landfills release various odors, attract disease vectors, and produce leachates that pollute
+ground water.
+
+Black soldier fly (BSF), Hermetia illucens, is an insect that has gained popularity among other
+insect-based bio-waste treatments for its effectiveness to convert bio-waste using its larvae. Biowaste biomass is consumed by the larvae, which then will be transformed into protein and fat of
+the larvae as well as its residue. The larvae is known to be having a high quality protein suitable
+for feeding chicken and fish, residue contains nutrients and organic matter that helps reduce soil
+depletion. Additionally, its effectiveness in reducing the risk of bacterial transmission through biowaste makes BSF a safe option for bio-waste treatment in farm level.
+
+Previously, BSF farming required wide spaces about 150 m2
+that made it difficult to rear in
+locations with limited spaces like urban areas. Moreover, the rearing method needs special care to
+adjust suitable condition (temperature and humidity) and frequent attention from laborers which
+generally take times in each procedure. For this reason, there was a need to establish an intelligent
+BSF rearing system.
+
+The Internet of Things (IoT) has begun to emerge as it has helped human in controlling and
+monitoring essential conditions using devices which are able to capture, evaluate and transmit
+information from the environment to the cloud, where the data will be stored. Environment
+monitoring system is one of the most important IoT systems which mainly includes data
+collections through sensors and data reviewing for short-term measure as well as remote
+management and observations.
+
+By using the IoT system to maintain the environmental condition i.e. temperature, relative
+humidity, light intensity and aeration of BSF larvae on its optimum level, data collection from the
+sensors needs to be obtained in real time to make sure that the data is accurate and representing
+the exact information of the environmental condition, as well as to be saved automatically to the
+database for certain period. This is to ensure that the user will have the proper information to
+interpret the insect’s environmental condition. Thus, data communication from the sensor to the
+database plays an important role in obtaining this need.
 This paper seeks to develop an automated solution to BSF rearing addressing two needs:
@@
     \item Controlling the environmental conditions, which is currently manual and labor-intensive.
-\item Remote monitoring of these conditions in real time.
+    \item Remote monitoring of these conditions in real time
 \end{enumerate}
 
+\section{RELATED WORK}
+
+\subsection{Nkozi University.}
+In 2021, Joseph Kasana implemented a World Bank funded BSF project in Nkozi university. The
+model has the eggs, larvae, pupa and adults in one setup. The setup (enclosure) consists of wooden
+cages covered with wire mesh. These he called the love cages. Each cage has a soaked sponge that
+provides the BSF with water and contributes towards humidity. The base of a love cage is open
+and underneath it is a drum. In this drum, pieces of wood planks are provided in which the adults
+lay eggs. The interior of the drum is always dark. The eggs are scraped off the planks and placed
+in containers containing feed (wet maize bran). They are thereafter taken to a different building
+called a larvaerium where they stay for four days until they become larvae. The larvae are dried
+and milled into a powder. The pupa are physically brought into the love cage very early in the
+morning (around 4:00 am) when temperatures are still low. This is to prevent any pupa that have
+become adults from becoming active and flying away. The entire setup is covered with a blue
+plastic. Joseph said this plastic is used to control both temperature and light intensity. Additionally,
+it was his belief that the Black Soldier Fly operates best under blue light. Joseph incurred a lot of
+losses with this set up and closed the project in November, 2022.
+
+\subsection{Marula Proteen Limited}
+Marula Proteen Limited practices BSF rearing on a large scale. They feed urban organic-waste to
+BSF larvae. After a short rearing period these larvae are harvested, dried and processed into high
+quality protein food for livestock production \cite{b1}. The pupa are taken to a greenhouse at another
+location (Namanve). According to the on-site agricultural engineer, the reason for the change in
+location is because there are some pests that are harmful to the eggs but liked by the pupa. The
+pupa are placed in cages in the greenhouse and provided with ideal conditions to encourage
+breeding. The greenhouse is fitted with sensors and a control panel to automatically control
+temperature, humidity and light intensity. A fog pump goes on when the humidity is too low, high
+energy lamps turn on when the temperatures are low and a motor controls the opening/closing of
+an aluminium foil to control light intensity. The eggs laid in-between planks in the cages are
+scraped off and taken to an incubator room where they are kept for four days until they develop
+into larvae. The incubator is also fitted with sensors to control temperature, light and aeration.
+
+\section{SOFTWARE AND COMPONENTS}
+\subsection{Node MCU esp 32}
+NodeMCU is an open-source LUA based firmware developed for the ESP8266 wifi chip. By
+exploring functionality with the ESP8266 chip, NodeMCU firmware comes with the ESP8266
+Development board/kit i.e. NodeMCU Development board. Since NodeMCU is an opensource platform, its hardware design is open for edit/modify/build. NodeMCU Dev Kit/board
+consist of ESP8266 wifi enabled chip. The ESP8266 is a low-cost Wi-Fi chip developed by
+Espressif Systems with TCP/IP protocol. Additionally, it contains the crucial elements of a
+computer: CPU, RAM, networking (WiFi), and even a modern operating system and SDK.
+That makes it an excellent choice for Internet of Things (IoT) projects of all kinds. It collects
+and transfers data from the sensors to the cloud based server [1] [2].
+\subsection{BH1750}
+The BH1750 is a calibrated digital light sensor IC that measures the incident light intensity and
+converts it into a 16-bit digital number. The sensor directly gives a digital output. The sensor
+output can be accessed through an I2C interface. It measures ambient light intensity and the
+measurement unit is Lux [3].
+\subsection{DHT22}
+The DHT-22 (also named as AM2302) is a digital-output relative humidity and temperature
+sensor. It uses a capacitive humidity sensor and a thermistor to measure the humidity and
+temperature of the surrounding air, and spits out a digital signal on the data pin [4].
+\subsection{Relay}
+A relay is a programmable electrical switch that can be controlled by a microcontroller. It is
+used to programmatically control the switching on/off of devices which use high voltage and/or
+high current. For this reason a relay can be thought of as a bridge between the microcontroller
+and high voltage devices [5].
+\subsection{Servo motor}
+Servo motors are great devices that can turn to a specified position. Usually, they have a servo
+arm that can turn 180 degrees. Using a microcontroller, we can tell a servo to go to a specified
+position and it will go there. As simple as that! Servo motors were first used in the Remote
+Control (RC) world, usually to control the steering of RC cars or the flaps on a RC plane. With
+time, they found their uses in robotics, automation, and of course, the Arduino world [5]. The
+servo motors will act as actuators when a certain condition is met
+
+\subsection{Firebase Realtime Database}
+The Firebase Realtime Database is a cloud-hosted database that lets you build rich, collaborative
+applications by allowing secure access to the database directly from client-side code. Data is
+persisted locally, and even while offline, realtime events continue to fire, giving the end user a
+responsive experience. When the device regains connection, the Realtime Database synchronizes
+the local data changes with the remote updates that occurred while the client was offline, merging
+any conflicts automatically. It provides a flexible, expression-based rules language, called Firebase
+Realtime Database Security Rules, to define how your data should be structured and when data
+can be read from or written to. When integrated with Firebase Authentication, developers can
+define who has access to what data, and how they can access it. It is a NoSQL database and as
+such has different optimizations and functionality compared to a relational database. The Realtime
+Database API is designed to only allow operations that can be executed quickly. This enables you
+to build a great realtime experience that can serve millions of users without compromising on
+responsiveness. Because of this, it is important to think about how users need to access your data
+and then structure it accordingly. Data is stored as JSON and synchronized in realtime to every
+connected client. When you build cross-platform apps with Apple platforms, Android, and
+JavaScript SDKs, all of clients share one Realtime Database instance and automatically receive
+updates with the newest data [1]
+\section{PROPOSED SYSTEM}
+\section{ENUMERATION}
+Efficient and reliable black soldier fly larvae bio-waste treatment requires a reliable estimate
+on the number of larval offspring dosed per unit of bio-waste and/or larvero (treatment crate),
+which is determined by laborious manual counting of young larvae \cite{e1}. Additionally, there is
+a tendency of BSF farmers to favor larger flies as they have a higher reproduction rate, the
+larvae are bigger and thus contain more protein than smaller larvae. Manual selection of such
+traits at an industrial level is currently infeasible due to the high numbers of larvae making it
+economically unviable \cite{e2}.
+Through the deployment of computer vision techniques together with deep learning methods;
+1. Larvae enumeration can be made more efficient and accurate.
+2. The process can be automated
+
+\section{CONCLUSION}
+
+\section*{Acknowledgment}
+
+We thank Phillip the Chief Technical Officer at Proteen for assistance with hardware like
+node MCU ESP32 for prototyping and Joseph Kasana for showing us the project at Nkozi University.
+
+\begin{thebibliography}{00}
+    \bibitem{b1}  "Proteen," [Online]. Available: https://weareproteen.com/. [Accessed 23 February 2023].
+    \bibitem{e2}  "Towards automatic enumeration of Black Soldier Fly Larvae offspring," [Online]. Available: https://www.eawag.com. [Accessed 23 February 2023].
+    \bibitem{e2}  M.F.Hansen, "Towards Machine Vision for Insect Welfare Monitoring and Behavioural Insights," Frontiers in Veterinary Science, vol. 9, 2022.
+\end{thebibliography}
 \end{document}

### 2023-03-14 abstract-intro/paper.tex
Update paper.tex

--- 2023-02-14 abstract-intro/paper.tex
@@
 % The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
+\usepackage{hyperref}
+\usepackage[utf8]{inputenc}
 \usepackage{cite}
@@
 \usepackage{xcolor}
+\usepackage{gensymb}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
     T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+\hypersetup{
+    colorlinks=true,
+    linkcolor=blue,
+    filecolor=black,      
+    urlcolor=blue,
+    citecolor=black
+    }
 
@@
 
-    \title{Low cost IOT based cloud solution for Intelligence Integrated Black fly rearing.}
+    \title{Low cost Intelligent Rearing of  Black Soldier Fly(BSF) based on cloud and Internet of Things(IOT).}
 
@@
 
-        \IEEEauthorblockN{1\textsuperscript{st} Shawal Mbalire}
+        \IEEEauthorblockN{Frank Ssemakula}
         \IEEEauthorblockA{\textit{School of Engineering,CEDAT} \\
@@
         Kampala, Uganda \\
-        mshawal49@icloud.com}
+        \href{mailto:semakulafrank@gmail.com}{semakulafrank@gmail.com}}
 
         \and
-        \IEEEauthorblockN{2\textsuperscript{nd} Mary Patience Namugwanya}
+        \IEEEauthorblockN{Bradley Alfred Mpeera Tuwmine}
         \IEEEauthorblockA{\textit{School of Engineering,CEDAT} \\
@@
         Kampala, Uganda \\
-        nmarypatience@gmail.com}
+        \href{mailto:bradleytumwine82@gmail.com}{bradleytumwine82@gmail.com}}
 
         \and
-        \IEEEauthorblockN{3\textsuperscript{rd} Bradley Alfred Mpeera Tuwmine}
+        \IEEEauthorblockN{Mary Patience Namugwanya}
         \IEEEauthorblockA{\textit{School of Engineering,CEDAT} \\
@@
         Kampala, Uganda \\
-        bradleytumwine82@gmail.com}
+        \href{mailto:nmarypatience@gmail.com}{nmarypatience@gmail.com}}
+
+        \and
+        \IEEEauthorblockN{Shawal Mbalire}
+        \IEEEauthorblockA{\textit{School of Engineering,CEDAT} \\
+        \textit{Makerere University}\\
+        Kampala, Uganda \\
+        \href{mailto:mshawal49@icloud.com}{mshawal49@icloud.com}\\
+        \href{shawalmbalire.com}{shawalmbalire.com}}\hspace{\linewidth}
+
     }
-
     \maketitle
@@
     \begin{abstract}
-        This paper aims to increase the production of black fly larvae for farmers to scale up by automating the monotonous and monitoring intesive tasks.
+     This paper proposes an IoT-based cloud solution for intelligent BSF (Black Soldier Fly) rearing.
+Internet of Things (IoT) is used for environmental condition monitoring to ensure optimal growing conditions and enable sensor data to be obtained in real-time.
+The system uses sensors such as temperature,humidity and light intensity.
+The data collected by the sensors is sent to a Firebase Real Time database.
+Streamlit python library is used to build a web app that provides an interface between the user and the Firebase Real Time database.
+The objective of this study is to demonstrate the feasibility of the proposed solution in optimizing BSF rearing and its potential contribution to sustainable food production and waste management practices.
+
+       %Black soldier fly(BSF), Hermetia illucens is a commonly and widespread fly of the family Stratiomyidae.
+Since the late 20th century, its larvae stage has increasingly gained attention due to its effective bio-waste conversion \cite{texbook}.
+Additionally, it has an excellent ability to transform waste into high quality protein.
+Used as alternative protein additives in animal feed which translates into an inexpensive clean and sustainable food source.
+Though effective, it requires certain environmental conditions that need to be monitored regularly to make sure the larvae can process the waste effectively.
+Several challenges remain to ensure that BSF farming is economically viable at different scales and can be widely implemented.Manual labor is required to ensure optimal conditions to rear the larvae, from aerating the feeding substrate to monitoring physical conditions during the growth cycle \cite{lamport94}.
+But, BSF farmers are not always on site yet the human resource is limited.
+Thus, an automated system with remote monitoring capability is needed to ease the monitoring process.
+
+        %Introduction:
+        % The Black Soldier Fly (BSF) has gained increasing attention in recent years as a sustainable source of protein due to its high nutritional value and efficient conversion of organic waste into protein.
+However, BSF rearing can be challenging, and monitoring critical parameters such as temperature, humidity, and light intensity is necessary to optimize the process and maximize production yields.
+In this paper, we present a low-cost IoT-based cloud solution for intelligent BSF rearing designed using ESP32, Firebase, and Streamlit.
+The objective of this study is to demonstrate the feasibility of the proposed solution in optimizing BSF rearing and its potential contribution to sustainable food production practices.
+
+        % The prototype capable of monitoring temperature, humidity, and light intensity. The collected data is transmitted to the cloud for analysis and optimization of the rearing process.
+
+        % The results demonstrate that the proposed IoT-based cloud solution can improve the efficiency and profitability of BSF rearing improving production yields and contributing to the development of sustainable food production practices.
+
+        % The low-cost IoT-based cloud solution developed in this study offers  real-time monitoring and analysis of critical parameters involved in BSF rearing.
+This allows farmers and businesses to make informed decisions to maximize production yields and optimize the rearing process.
+Furthermore, the system's low cost and ease of use make it an attractive option for small-scale farmers and businesses seeking to enter the insect protein industry.
+
+       \textbf{Keywords - BSF ,Intelligent Rearing, IoT, Cloud}
     \end{abstract}
-
-    \begin{IEEEkeywords}
-        black fly soldier fly larvea,iot
-    \end{IEEEkeywords}
 
@@
 
+Bio-waste management is one of the main global challenges of our time, with significant repercussions on human and environmental health related to sanitary issues, pollution of ground water, and emission of greenhouse gases.
+As global population and consumption rise, bio-waste production is also projected to increase significantly.
+
+Conventional methods of dealing with bio-waste, including open dumping in less economically developed countries or landfilling are not equipped with means to capture green house gases such as methane, carbon dioxide and nitrogen dioxide worsen the global warming crisis.
+Besides, landfills release various odors, attract disease vectors, and produce leachates that pollute ground water \cite{texbook}.
+
+Black Soldier Fly (BSF), Hermetia illucens, is an insect that has gained popularity among other insect-based bio-waste treatments for its effectiveness to convert bio-waste using its larvae.
+Bio-waste biomass is consumed by the larvae, which is then transformed into protein and fat of the larvae as well as its residue.
+The larvae is known to be having a high quality protein suitable for livestock feeding chicken and fish, residue contains nutrients and organic matter that helps reduce soil depletion.
+Additionally, its effectiveness in reducing the risk of bacterial transmission through bio-waste makes BSF a safe option for bio-waste treatment at the farm.
+
+Previously, BSF farming required wide spaces about 150 m$^2$ that made it difficult to rear in locations with limited spaces like urban areas.
+Moreover, the rearing method needs special care to adjust suitable condition (temperature, light intensity and humidity) and frequent attention from laborers which generally take times in each procedure.
+For this reason, there is a need to establish an intelligent BSF rearing system \cite{lamport94}.
+
+The emergence of Internet of Things (IoT) has helped humans in controlling and monitoring essential conditions.
+This is possible using devices which capture, evaluate and transmit information from the environment to the cloud, where the data will be stored.
+Environment monitoring system is one of the most important IoT systems which mainly includes data collections through sensors and data reviewing for short-term measure as well as remote management and observations.
+
+IoT systems maintain the environmental conditions i.e.
+temperature, relative humidity and light intensity of environment at optimum levels for rearing of the BSF larvae.
+Data collection from the sensors needs to be obtained in real time.
+This ensures that the data is accurate and represents the exact information of the environmental condition and is saved automatically to the database for a certain period.
+This is to ensure that the user will have the proper information to interpret the insect’s environmental conditions \cite{b2}.
+Thus, data communication from the sensor to the database plays an important role in obtaining this need.
+This paper seeks to develop an automated solution to BSF rearing addressing two needs:
+\begin{enumerate}
+\item Controlling the environmental conditions, which is currently manual and labor-intensive. 
+\item Remote monitoring of these conditions in real time.
+\end{enumerate}
+
+\section{background}
+
+\subsection{Nkozi University}
+In 2021, Nkozi Univesity implemented a World Bank funded BSF project. The
+model has the eggs, larvae, pupa and adults in one setup. The setup (enclosure) consists of wooden
+cages covered with wire mesh(love cages).Each cage has a blue plastic container with a soaked sponge that
+provides the BSF with water. The base of a love cage is open
+and underneath it is a drum as shown in Figure 1. In this drum, pieces of wood planks are provided in which the adults
+lay eggs. The interior of the drum is always dark. The eggs are scraped off the planks and placed
+in containers containing feed (wet maize bran). They are thereafter taken to a different building
+called a larvaerium where they stay for four days until they become larvae. The larvae are dried
+and milled into a powder. The pupa are physically brought into the love cage very early in the
+morning (around 4:00 am) when temperatures are still low. This is to prevent any pupa that have
+become adults from becoming active and flying away.
+The entire setup is covered with a blue tarpin.
+This tarpin is used to control both temperature and light intensity.
+Additionally, the University farmers believed that the Black Soldier Fly operates best under blue light.
+The University incurred a lot of losses with this set up and closed the project in November, 2022.
+
+% \begin{figure}[h]
+%     \begin{center}
+%         \includegraphics[width=\linewidth]{nkozi exterior.PNG}
+%         \caption{\large System setup}
+%     \end{center}
+% \end{figure}
+
+\begin{figure}[h]
+    \begin{center}
+        \includegraphics[width=\linewidth]{nkozi1.png}
+        \caption{\large Nkozi University System interior}
+    \end{center}
+\end{figure}
+
+\subsection{Marula Proteen Limited}
+Marula Proteen Limited practices BSF rearing on a large scale. They feed urban organic-waste to
+BSF larvae. After a short rearing period these larvae are harvested, dried and processed into high quality protein food for livestock production. The pupa are taken to a greenhouse at another
+location (Namanve) as shown in Figure 2. According to the on-site agricultural engineer, the reason for the change in
+location is because there are some pests that are harmful to the eggs but liked by the larvae. The
+pupa are placed in cages in the greenhouse where they develop into adults.
+The adults are provided with ideal conditions to encourage breeding.
+The greenhouse is fitted with sensors and a control panel to automatically control
+temperature, humidity and light intensity. A fog pump goes on when the humidity is too low, high
+energy lamps turn on when the temperatures are low and a motor (Figure 3) controls the opening/closing of
+a shade to control light intensity. The eggs laid in-between planks in the cages are
+scraped off and taken to an incubator room where they are kept for four days until they develop
+into larvae. The incubator is also fitted with sensors to control temperature, light and aeration.
+
+\begin{figure}[h]
+    \begin{center}
+        \includegraphics[width=\linewidth]{greenhouse1.PNG}
+        \caption{\large Greenhouse exterior}
+    \end{center}
+\end{figure}
+
+\begin{figure}[h]
+    \begin{center}
+        \includegraphics[width=\linewidth]{greenhouse2.PNG}
+        \caption{\large Motor in greenhouse}
+    \end{center}
+\end{figure}
+
+\section{proposed system}
+%This paper presents a control and remote monitoring system for BSf rearing.
+The system  controls  light intensity, humidity and temperature which are environmental conditions that greatly affect the survival and breeding of the Black Soldier Fly.
+Additionally, the system transmits the data obtained from the sensors and stores it in an online database enabling real time monitoring of the parameters.
+The sensor data is stored in a Firebase Real Time Database.
+The project software is programmed and run in Arduino IDE.
+
+The block diagram of the proposed system is shown in Figure 4.
+The system uses the NodeMCU ESP32s as the microcontroller.
+The temperature and humidity readings from a bunch of DHT22 sensors in the room are averaged to two temperature and humidity values which are fed through single bus communication protocol to the microcontroller.The data from the BH1750 is communicated through I2C protocol and the readings appropriately converted to light intensity in lux.
+
+\begin{table}[ht]
+\caption{System parameters \cite{proietti2022non}}
+\begin{center}
+\begin{tabular}{|p{0.15\linewidth}|p{0.15\linewidth}|p{0.15\linewidth}|p{0.15\linewidth}|p{0.15\linewidth}|}
+
+\hline
+{\textbf{Parameter}} & {\textbf{Acceptable range}} & {\textbf{Units}} \\
+\hline
+Temperature & 30 - 35 & \degree C \\
+\hline
+Humidity & 65.0 - 75.0 &  RH\% \\
+\hline
+Light Intensity &  550-10000 & Lux \\
+\hline
+
+\end{tabular}
+\label{tab1}
+\end{center}
+\end{table}
+The system pseudocode is illustrated in Figure 5.
+The microcontroller is programmed in micro python to control 3 relays.
+One relay switches a servo motor that is connected via pulleys and strings to a shade that covers the system thus controlling the light intensity.
+The other relay runs a fog motor machine that simultaneously increases humidity and decreases temperature.
+The last relay runs a high energy lamp that increases temperature as well as light intensity.Therefore, the system maintains the parameters in the ranges shown in Table 1.
+
+The microcontroller sends data over a Wi-Fi connection to Firebase real time database and listens for remote commands from a web app interface created using the Streamlit Python library.
+The systems allows for push buttons to act as interrupts for manual switching.
+
+\begin{figure}[h]
+    \begin{center}
+        \includegraphics[width=\linewidth]{DIAGRAM.png}
+        \caption{\large  Block diagram}
+    \end{center}
+\end{figure}
+
+% \begin{figure}[h]
+%     \begin{center}
+%         \includegraphics[width=\linewidth]{pushbuttons.png}
+%         \caption{\large Circuit diagram}
+%     \end{center}
+% \end{figure}
+
+The microcontroller sends data to the database and reads instructions from database to switch the shade,lights or fog machine on and off every 5 minutes.
+The database security only allows input from the firebase web application and is accessed by the ESP32s.
+The user logs into a web application which shows current temperature, light and humidity values as well as the state (on/off) of the shade,lights and fog machine.
+Toggle buttons are used to switch state values which update over the database and in turn are sent to the microcontroller in less than 5 minutes.
+\begin{figure}
+    \begin{center}
+        \includegraphics[width=\linewidth]{FLOWCHART.png}
+        \caption{\large Flow chart diagram}
+    \end{center}
+\end{figure}
+
+\section{methodology}
+
+\subsection{Firebase Real Time Database}
+The Firebase Realtime Database is a cloud-hosted database that lets you build rich, collaborative
+applications by allowing secure access to the database directly from client-side code. Data is
+persisted locally, and even while offline, real time events continue to fire, giving the end user a
+responsive experience. When the device regains connection, the Realtime Database synchronizes
+the local data changes with the remote updates that occurred while the client was offline, merging
+any conflicts automatically. It provides a flexible, expression-based rules language, called Firebase
+Realtime Database Security Rules, to define how your data should be structured and when data
+can be read from or written to. When integrated with Firebase Authentication, developers can
+define who has access to what data, and how they can access it. It is a NoSQL database and as
+such has different optimizations and functionality compared to a relational database. The Realtime
+Database API (Application Programming Interface) is designed to only allow operations that can be executed quickly. This enables you
+to build a great realtime experience that can serve millions of users without compromising on
+responsiveness. Because of this, it is important to think about how users need to access your data
+and then structure it accordingly. Data is stored as JSON (Java Script Object Notation) and synchronized in realtime to every
+connected client. When you build cross-platform apps with Apple platforms, Android, and
+JavaScript SDKs, all of the clients share one Realtime Database instance and automatically receive
+updates with the newest data \cite{b3}.
+
+\subsection{Streamlit Python library \cite{streamlit}}
+Streamlit is an open-source Python library that makes it easy to create and share beautiful, custom web apps for machine learning and data science.
+In just a few minutes you can build and deploy powerful data apps.
+One of the features of the library is the  Streamlit's Community Cloud.
+It is an open and free platform for the community to deploy, discover, and share Streamlit apps and code with each other.
+
+\subsection{Node MCU ESP32s}
+NodeMCU is an open-source LUA based firmware developed for the ESP32s Wi-Fi chip. By
+exploring functionality with the ESP32s chip, NodeMCU firmware comes with the ESP32s
+Development board/kit i.e. NodeMCU Development board. Since NodeMCU is an opensource platform, its hardware design is open for edit/modify/build. NodeMCU Dev Kit/board
+consist of ESP32s Wi-Fi enabled chip. The ESP32s is a low-cost Wi-Fi chip developed by
+Espressif Systems with TCP/IP protocol. Additionally, it contains the crucial elements of a
+computer: CPU, RAM, networking (WiFi), and even a modern operating system and SDK (Software Development Kit).
+That makes it an excellent choice for Internet of Things (IoT) projects of all kinds. It collects
+and transfers data from the sensors to the cloud based server\cite{b4}\cite{b5}.
+
+\subsection{BH1750}
+The BH1750 is a calibrated digital light sensor IC that measures the incident light intensity and
+converts it into a 16-bit digital number. The sensor directly gives a digital output that can be accessed through an I2C interface. It measures ambient light intensity and the
+measurement unit is Lux \cite{b6}.
+
+\subsection{DHT22}
+The DHT-22 (also named as AM2302) is a digital-output relative humidity and temperature
+sensor. It uses a capacitive humidity sensor and a thermistor to measure the humidity and
+temperature of the surrounding air, and gives a digital signal on the data pin \cite{b7}.
+
+\subsection{Relays}
+A relay is a programmable electrical switch that can be controlled by a microcontroller. It is
+used to programmatically control the switching on/off of devices which use high voltage and/or
+high current. For this reason a relay can be thought of as a bridge between the microcontroller
+and high voltage devices \cite{b8}.
+
+\subsection{Servo motor}
+Servo motors are great devices that can turn to a specified position. Usually, they have a servo
+arm that can turn 180 degrees. Using a microcontroller, we can tell a servo to go to a specified
+position and it will go there. As simple as that! Servo motors were first used in the Remote
+Control (RC) world, usually to control the steering of RC cars or the flaps on a RC plane. With
+time, they found their uses in robotics, automation, and of course, the Arduino world \cite{b8}. The
+servo motors represent the single phase induction motors used for the fog pump and shade control.
+
+% \section{Future Work}
+
+% \begin{enumerate}
+%     \item Deploy computer vision techniques together with deep learning methods;
+%     \begin{itemize}
+%         \item To make larvae enumeration more efficient and accurate.
+%         \item To automate the enumeration process.
+%     \end{itemize}
+%     Efficient and reliable black soldier fly larvae bio-waste treatment requires a reliable estimate on the number of larval offspring dosed per unit of bio-waste and/or larvero (treatment crate), which is determined by laborious manual counting of young larvae \cite{b9}.
+Additionally, there is a tendency of BSF farmers to favor larger flies as they have a higher reproduction rate, the larvae are bigger and thus contain more protein than smaller larvae.
+Manual selection of such traits at an industrial level is currently infeasible due to the high numbers of larvae making it economically unviable \cite{b0}.
+%     \item Design a more efficient switching circuit system that works for longer switch cycles compared to relays whose contacts melt and weld together for more frequent switching.
+%     \item Add GSM compatibility to remote monitoring using a SIM800L module with 3G capabilities to increase coverage.
+%     \item Create a mobile application for users to interface with the system.   
+% \end{enumerate}
+
+\section{conclusion}
+
+Waste is expected to increase with the increasing population hence waste processing and management is therefore very critical to protect our environment. This is inline with SDG 13.
+
+In this study, an automatic control and remote monitoring system using IoT technologies is proposed.
+The system improves the efficiency of BSF larvae production with a significant reduction in time and labor.
+Moreover, it uses low-cost digital devices and is easily accessible via a web application.
+This is a major step inline with improving efficiency in production lines based on food and environmental conditions.
+
+Therefore, the proposed IoT system enhances larvae production which in turn leads to an advancement in organic waste processing and management.
+
+%\nocite{*}
+%\bibliographystyle{IEEEtran}
+%\bibliography{references}
+\begin{thebibliography}{99}
+\bibitem{texbook}
+M.
+C.
+K.
+M.
+M.
+G.
+K.
+K.
+Kevin Urrutria Avila, "Development and Testing of a Smart BIn toward Automated rearing of Black Soldier Fly Larvae," in IEEE 18th International Conference on Automation Science and Engineering (CASE), Mexico City, 2022.
+
+\bibitem{lamport94}
+M.
+O.
+H.
+K.
+H.
+B.
+A.
+D.
+P.
+W.
+T.
+Sarah Alyaa Tsaabitah, "Data Communication using MQTT for Black Soldier Fly Larvae Monitoring System," in International Conference on Wireless and Telematics (ICWT), Bandung, 2022.
+
+% \bibitem{b1}
+% N.
+S.
+A.
+T.
+S.
+S.
+T.
+J.
+N.
+C.
+Suttida Suwannayod, "Semi-automated IoT based Cabinet for Rearing Black Soldier Fly Larvae (BSFL)," in 7th International Conference on Information and Network Technologies (ICINT), Chiang Mai, 2022.
+
+\bibitem{b2}
+[4] 	M.
+R.
+T.
+K.
+M.
+Abdulmjeed Hassan Adam, "Low-Cost Green Power Predictive Farming Using IOT and Cloud Computing," in International Conference on Vision Towards Emerging Trends in Communication and Networking (ViTECoN), Rajahmundry,, 2019.
+
+\bibitem{b3}
+"Firebase Realtime Database," Firebase, [Online]. Available: https://firebase.google.com/docs/database. [Accessed 24 February 2023].
+
+\bibitem{b4}
+"Introduction to NodeMCU," [Online]. Available: https://www.electronicwings.com/nodemcu/introduction-to-nodemcu. [Accessed 23 February 2023].
+
+\bibitem{b5}
+"NodeMCU ESP32s," [Online]. Available: https://www.make-it.ca/nodemcu-details-specifications. [Accessed 23 February 2023].
+
+\bibitem{b6}
+M.
+Damirchi, "Interfacing BH1750 Light Intensity Sensor with Arduino," [Online].
+Available: https://electropeak.com/learn/interfacing-bh170-light-intensity-sensor-with-arduino.
+[Accessed 23 February 2023].
+
+\bibitem{b7}
+codebender-cc, "How to Use DHT-22 Sensor- Arduino Tutorial," [Online].
+Available: https://www.google.com/amp/s/www.instructables.com/How-to-Use-DHT-22-Sensor-Arduino-Tutorial.
+[Accessed 23 February 2023].
+
+\bibitem{b8}
+"Arduino Relay,"[Online]. Available: https://arduinogetstarted.com/tutorials/arduino-relay. [Accessed 23 February 2023].
+
+\bibitem{b9}
+"Towards automatic enumeration of Black Soldier Fly Larvae offspring," [Online]. Available: https://www.eawag.com. [Accessed 23 February 2023].
+
+\bibitem{b0}
+M. F. Hansen, "Towards Machine Vision for Insect Welfare Monitoring and Behavioural Insights," Frontiers in Veterinary 
+Science, vol. 9, 2022.
+
+\bibitem{proietti2022non}
+M. Proietti, A. Marini, A. Garinei, G. Rossi, F. Bianchi, M. Marconi,
+S. Discepolo, M. Martarelli, M. T. Calcagni, G. Zeni et al., “Non-invasive
+measurements for characterization of hermetia illucens (bsf) life cycle in
+rearing plant,” in 2022 IEEE Workshop on Metrology for Agriculture and
+Forestry (MetroAgriFor). IEEE, 2022, pp. 223–228
+
+\bibitem{tsaabitah2022data} S. A. Tsaabitah, M. O. Hasanuddin, K. H. Burhan, A. D. Permana, and
+W. Trusaji, “Data communication using mqtt for black soldier fly larvae
+monitoring system,” in 2022 8th International Conference on Wireless
+and Telematics (ICWT). IEEE, 2022, pp. 1–5.
+
+\bibitem{uddin2022iot} M. A. Uddin, U. K. Dey, S. A. Tonima, and T. I. Tusher, “An iot-based
+cloud solution for intelligent integrated rice-fish farming using wireless
+sensor networks and sensing meteorological parameters,” in 2022 IEEE
+12th Annual Computing and Communication Workshop and Conference
+(CCWC). IEEE, 2022, pp. 0568–0573.
+
+\bibitem{rabell2021review} V.
+C.
+Rabell, C.
+Gutierrez-Antonio, J.
+F.
+G.
+Trejo, and A.
+A.
+Feregrino-Perez, “A review on processes for whey and dairy wastewater treatment and valorization,” in 2021 XVII International Engineering Congress
+(CONIIN). IEEE, 2021, pp. 1–6.
+
+\bibitem{b1} S. Suwannayod, S. S. Ramasamy, N. Suyaroj, A. Tananchana, S. Siriphen,
+T. Jenrungrod, and N. Chakpitak, “Semi-automated iot based cabinet
+for rearing black soldier fly larvae (bsfl),” in 2022 7th International
+Conference on Information and Network Technologies (ICINT). IEEE,
+2022, pp. 80–84.
+
+\bibitem{sabir2020electrically} M. O. Sabir, P. Verma, P. Maduri, and K. Kushagra, “Electrically
+controlled artificial system for organic waste management using black
+soldier flies with iot monitoring,” in 2020 2nd International Conference
+on Advances in Computing, Communication Control and Networking
+(ICACCCN). IEEE, 2020, pp. 871–875.
+
+\bibitem{avila2022development} K. U. Avila, M. Campbell, K. Mauck, M. Gebiola, and K. Karydis,
+“Development and testing of a smart bin toward automated rearing of
+black soldier fly larvae,” in 2022 IEEE 18th International Conference on
+Automation Science and Engineering (CASE). IEEE, 2022, pp. 1238–
+1243.
+\bibitem{streamlit}{"Official Streamlit Website" Available: https://streamlit.io/}[Accessed 27 February 2023
+
+\end{thebibliography}
 \end{document}
